---
title: "Shock comparison"
author: "Juho Koistinen"
date: "2022-09-28"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
liblist <- c("readr", "tidyverse", "lubridate", "fbi", "readxl", "vars", "svars", "svarmawhf", "lemon") 
void <- lapply(liblist, library, character.only = TRUE)

rotmat <- function(x, n){
  
  rot_ix <- combn(n,2)
  final_mat <- diag(n)
  
  for(jj in 1:ncol(rot_ix)){
    rot_mat <- matrix(c(cos(x[jj]), -sin(x[jj]), sin(x[jj]), cos(x[jj])), 2, 2)
    temp_mat <- diag(n)
    temp_mat[rot_ix[,jj], rot_ix[,jj]] <- rot_mat
    final_mat <- final_mat %*% temp_mat
  }
  
  final_mat
}

ff <- function(x, zero_ix, input_mat){
  
  row_ix <- if(is.null(dim(zero_ix))) zero_ix[1] else zero_ix[,1]
  col_ix <- if(is.null(dim(zero_ix))) zero_ix[2] else zero_ix[,2]
  sum(sqrt(diag(input_mat[row_ix,] %*% rotmat(x, ncol(input_mat))[, col_ix])^2))
}

get_irf <- function(..., id.type = c("chol", "n_gaus", "fevd_id"), n_ahead, zero_rest = NULL, hrz = 15){
  
  var_out <- vars::VAR(...)
  nobs <- dim(var_out$y)[1]
  n_var <- dim(var_out$y)[2]
  if(id.type=="chol"){
    bmat <- var_out %>% residuals %>% var %>% chol %>% t
  } else if(id.type=="n_gaus"){
    rest_mat <- matrix(NA, n_var, n_var)
    rest_mat[zero_rest[1], zero_rest[2]] <- 0
    svar_obj <- svars::id.ngml(var_out, restriction_matrix = rest_mat)
    bmat <- svar_obj$B
    fevd_var <- fevd(svar_obj)
    if(!is.null(zero_rest)) lratio <- svar_obj$lRatioTest
  } else if(id.type=="fevd_id"){
    chol_fac <- var_out %>% residuals %>% var %>% chol %>% t
    irf_i <- var_out %>% irf(boot=FALSE, n.ahead = n_ahead, ortho = FALSE) %>% .$irf %>%
      reduce(cbind) %>% t %>% c %>% array(dim=c(n_var, n_var, n_ahead+1))
    arg_max <- matrix(0, n_var, n_var)
    for(h in 1:(hrz+1)){
      for(tau in 1:h){
        arg_max <- crossprod(irf_i[1,,tau]%*%chol_fac) + arg_max
      }
    }
    gamma_out <- matrix(0, n_var, 1)
    gamma_out[-zero_rest,1] <- eigen(arg_max[-zero_rest,-zero_rest])$vector[,1]

    bmat <- diag(n_var)
    bmat[,1] <- gamma_out
    bmat <- chol_fac%*%bmat
  } else{
    stop("Specify identification scheme correctly")
  }
  irf_out <- var_out %>% irf(boot=FALSE, n.ahead = n_ahead, ortho = FALSE) %>% .$irf %>%
    reduce(cbind) %>% t %>% c %>% array(dim=c(n_var, n_var, n_ahead+1))
  list_out <- list(irf = unclass(pseries(irf_out, n_ahead)%r%bmat), 
                   bmat = bmat, 
                   resids = residuals(var_out))
  if(id.type=="n_gaus"){ 
    list_out$fevd <- fevd_var
    if(!is.null(zero_rest)) list_out$lratio <- lratio
  }
  return(list_out)
}

plot_irf <- function(irf_arr, var_name, shock_name){
  n_var <- dim(irf_arr)[1]
  n_shock <- dim(irf_arr)[2]
  n_ahead <- dim(irf_arr)[3]-1
  tibble(irf = c(irf_arr),
         variable = var_name %>% 
           factor(levels = var_name) %>% 
           rep((n_ahead+1)*n_shock),
         shock = shock_name %>% 
           factor(levels=shock_name) %>% 
           rep(each=n_var) %>% 
           rep(n_ahead+1),
         months = rep(0:n_ahead, each = n_var*n_shock)) %>% 
    ggplot(aes(x=months, y = irf)) +
    geom_line() +
    geom_hline(yintercept = 0, size = 0.15) +
    facet_grid(variable ~ shock, scales = "free_y") +
    facet_rep_grid(variable ~ shock, scales = "free_y", repeat.tick.labels = 'left') +
    scale_x_continuous(breaks = seq(12, n_ahead, by = 12), expand = c(0,0)) +
    scale_y_continuous(n.breaks = 5) +
    theme(legend.position = "none", 
          axis.text.x = element_text(angle = 0),
          axis.title.y = element_blank(),
          panel.grid.major = element_blank(),
          panel.spacing = unit(.5, "lines"),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          strip.background = element_blank(),
          axis.line = element_line(colour = "black"))
}

norm_irf <- function(irf_arr, norm_int, norm_scm = c("surp", "news")){

  n_var <- dim(irf_arr)[1]
  if(norm_scm=="surp"){
    irf_arr <- irf_arr[,1,,drop=FALSE]/irf_arr[n_var,1,1]*norm_int
  } else if(norm_scm=="news"){
    irf_arr <- irf_arr[,1,,drop=FALSE]/max(irf_arr[n_var,1,])*norm_int
  }
  irf_arr
}

```

# Introduction and preliminaries

This document summarizes the results from different VAR specifications, which use different monetary policy shock measures to uncover the dynamic effects of monetary policy.

The benchmark VAR consists of four widely used monetary policy variables:
$$
z_t = (100\cdot\log IP_t, 100\cdot\log CPI_t,EBP_t, FFR_t)'.
$$
The underlying assumption is that the policy equation is given as
$$
FFR_t = f(\Omega_t)+\varepsilon_t^{mp},
$$
where the deviation from the policy rate can be divided into a true surprise and anticipated component, known by public $q$ months ahead

$$
\varepsilon_t^{mp} = \varepsilon_t^{mps} + \varepsilon_{t-q}^{news}.
$$

To identify both components of the error to $FFR_t$, the baseline VAR is augmented with a monetary policy residual, $MPR_t\approx\varepsilon_t^{mps}+\varepsilon_{t-q}^{news}$, which reveals the monetary news/forward guidance component:
$$
y_t = (z_t', MPR_t)'.
$$

```{r load data, include=FALSE}
n_ahead <- 48
bs_data <- read_excel(path = "./local_data/FOMC_Bauer_Swanson.xlsx", 
                      sheet = "Monthly SVAR Data") %>% 
  rename(date = ...1, GS2 = `2y Treas`) %>% 
  mutate(date = ymd(str_remove(date, " UTC")),
         LIP = 100*log(IP),
         LCPI = 100*log(CPI))
  
ramey_rep <- read_excel(path = "./local_data/Monetarydat_ramey.xlsx", 
                        sheet = "Monthly") %>% 
  mutate(DATES = substr(DATES, 1, 4) %>% 
           paste0(c(rep("0", 9), rep("", 3)), 1:12, "01") %>% ymd(),
         LIP = 100*LIP,
         LCPI = 100*LCPI) %>% 
  rename(date = DATES)

fred_md <- fredmd("http://files.stlouisfed.org/files/htdocs/fred-md/monthly/current.csv",
                  transform = FALSE,
                  date_start = ymd(19720101)) %>%
  as_tibble() %>% 
  mutate(LIP = 100*log(INDPRO),
         LCPI = 100*log(CPIAUCSL),
         DLCPI = c(rep(NA, 12), diff(LCPI, 12)),
         DLIP = c(NA, diff(LIP))) %>% 
  filter(date>ymd(19721201))

ebp <- read_csv("https://www.federalreserve.gov/econres/notes/feds-notes/ebp_csv.csv")
fred_md$EBP <- ebp$ebp[1:nrow(fred_md)]

fred_md <- list(fred_md, readRDS("local_data/shock_tbl.rds"), dplyr::select(bs_data, date, GS2)) %>% 
  reduce(left_join, by = "date")

svarma_data <- fred_md %>% dplyr::select(date, LIP, LCPI, EBP, FEDFUNDS) %>% 
  filter(date>=ymd(19821001), date<ymd(20080101)) %>% 
  mutate_if(is.numeric, ~residuals(lm(.x~1+I(1:n())))) %>% 
  #mutate_if(is.numeric, ~.x-mean(.x)) %>%
  dplyr::select(-date)
saveRDS(svarma_data, "local_data/svarma_data.rds")
  
```

```{r plot, echo=FALSE}
fred_md %>%
  dplyr::select(date, LIP, LCPI, FEDFUNDS, EBP, resid_full) %>% 
  mutate(resid_full=cumsum(resid_full)) %>% 
  filter(date>=ymd(19821001), date<ymd(20080101)) %>%
  #mutate_at(vars(starts_with("L")), ~residuals(lm(.~1+I(1:n())))) %>% 
  pivot_longer(-date, names_to = "Variable", values_to = "Value") %>% 
  ggplot(aes(date, Value, color = Variable)) + 
  geom_line() + 
  facet_grid(factor(Variable, levels = c("LIP", "LCPI", "FEDFUNDS", "EBP", "resid_full")) ~ ., scales = "free_y") + 
  scale_x_date(date_labels = "%b %Y",date_breaks = "1 year", expand = c(10^-2,1) ) + 
  theme(legend.position = "none", 
      axis.text.x = element_text(angle = 90),
      axis.title.x = element_blank(),
      axis.title.y = element_blank()) +
    ggtitle("Raw Data")
```

# Identification

We entertain three identification schemes:

1. Internal instrument/recursive. $MPS_t$ is ordered first and the model is identified recursively. This gives results consistent with the external instrument/Proxy-SVAR approach. Only the conventional MP shock is identified and this is primarily used for comparison to the results using identification by non-Gaussianity.

2. Identification by non-Gaussianity. The aim is to identify structural shocks both to $FFR_t$ and $MPS_t$, where the former is the conventional and the latter is an anticipated monetary news shock. The identification is achieved by assuming shock non-Gaussianity combined with the short-run restriction that the news shock does not have contemporaneous effect on $MPS_t$.

3. FEVD. Only news shock is identified using this method. This method identifies the news shock as the one that maximizes the FEV of $MPR_t$ in a given forecast horizon. Details [here](https://assets.aeaweb.org/asset-server/articles-attachments/aer/data/oct2013/20110331_app.pdf).


# 2y Gov't bond
```{r gs2, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, GS2, LIP, LCPI, EBP, FEDFUNDS) %>% 
  filter(complete.cases(.), date<ymd(20190101), date>=ymd(19821001)) %>%
  mutate_if(is.numeric, ~.x-mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r gs2b, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("2-yr gov't bond, sample:", 
      svar_data %>% slice(1) %>% .$date, "--",
      svar_data %>% slice(n()) %>% .$date, sep = " "),
      subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                       "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```


# Romer and Romer (2004)
The Romer and Romer (2004) shock is expected to be short-lived and not to contain a forward guidance component, which would show up in the delayed response of FFR.

```{r rr04, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, resid_full, LIP, LCPI, EBP, FEDFUNDS) %>% 
  mutate(resid_full = cumsum(coalesce(resid_full, 0)) + resid_full*0) %>%
  filter(complete.cases(.), date>=ymd(19821001)) %>%
  mutate_if(is.numeric, ~.x-mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r rr04b, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("RR shock, sample:", 
                svar_data %>% slice(1) %>% .$date, "--",
                svar_data %>% slice(n()) %>% .$date, sep = " "),
          subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                           "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```

# Gertler and Karadi (2015)
```{r gk15, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, mp1_tc, LIP, LCPI, EBP, FEDFUNDS) %>% 
  mutate(mp1_tc = cumsum(coalesce(mp1_tc, 0)) + mp1_tc*0) %>% 
  filter(complete.cases(.), date>=ymd(19821001)) %>%
  mutate_if(is.numeric, ~.x - mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r gk15b, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("GK shock (1), sample:", 
                svar_data %>% slice(1) %>% .$date, "--",
                svar_data %>% slice(n()) %>% .$date, sep = " "),
          subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                           "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```

```{r gk15bb, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, ff4_tc, LIP, LCPI, EBP, FEDFUNDS) %>% 
  mutate(ff4_tc = cumsum(coalesce(ff4_tc, 0)) + ff4_tc*0) %>% 
  filter(complete.cases(.), date>=ymd(19821001)) %>%
  mutate_if(is.numeric, ~.x - mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r gk15bbb, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("GK shock (2), sample:", 
                svar_data %>% slice(1) %>% .$date, "--",
                svar_data %>% slice(n()) %>% .$date, sep = " "),
          subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                           "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```

# Bu, Rogers and Wu (2021)

```{r bgw21, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, BRW_monthly, LIP, LCPI, EBP, GS2) %>% 
  #mutate(BRW_monthly = cumsum(coalesce(BRW_monthly, 0)) + BRW_monthly*0) %>% 
  filter(complete.cases(.), date>=ymd(19821001)) %>% #, date<ymd(20090101)) %>%
  mutate_if(is.numeric, ~.x - mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r bgw21b, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("BRW shock, sample:", 
                svar_data %>% slice(1) %>% .$date, "--",
                svar_data %>% slice(n()) %>% .$date, sep = " "),
          subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                           "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```

# Miranda-Agrippino and Ricco (2021)

```{r mar21, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, MM_IV1, LIP, LCPI, EBP, FEDFUNDS) %>% 
  filter(complete.cases(.), date>=ymd(19821001)) %>%
  mutate_if(is.numeric, ~.x - mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r MAR21b, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("MAR21 shock (1), sample:", 
                svar_data %>% slice(1) %>% .$date, "--",
                svar_data %>% slice(n()) %>% .$date, sep = " "),
          subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                           "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```

```{r MAR21bb, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, MM_IV5, LIP, LCPI, EBP, FEDFUNDS) %>% 
  filter(complete.cases(.), date>=ymd(19821001)) %>%
  mutate_if(is.numeric, ~.x - mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r MAR21bbb, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("MAR21 shock (2), sample:", 
                svar_data %>% slice(1) %>% .$date, "--",
                svar_data %>% slice(n()) %>% .$date, sep = " "),
          subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                           "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```

# Jarocinski (2022)

```{r jaro22, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, u1, LIP, LCPI, EBP, FEDFUNDS) %>% 
  mutate(u1 = cumsum(coalesce(u1, 0)) + u1*0) %>% 
  filter(complete.cases(.), date>=ymd(19821001)) %>%
  mutate_if(is.numeric, ~.x - mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r jaro22b, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("Jaro22 shock, sample:", 
                svar_data %>% slice(1) %>% .$date, "--",
                svar_data %>% slice(n()) %>% .$date, sep = " "),
          subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                           "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```

# Aruoba and Drechsel (2022)

```{r ad22, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, Shock, LIP, LCPI, EBP, FEDFUNDS) %>%
  filter(complete.cases(.), date>=ymd(19821001)) %>%
  mutate_if(is.numeric, ~.x - mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r AD22, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("AD22 shock, sample:", 
                svar_data %>% slice(1) %>% .$date, "--",
                svar_data %>% slice(n()) %>% .$date, sep = " "),
          subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                           "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```

# Bauer and Swanson (2022)

```{r bs22, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, MPS, LIP, LCPI, EBP, FEDFUNDS) %>%
  mutate(MPS = scale(MPS)) %>% 
  filter(complete.cases(.), date>=ymd(19821001)) %>%
  mutate_if(is.numeric, ~.x - mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r BS22b, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("BS22 shock, sample:", 
                svar_data %>% slice(1) %>% .$date, "--",
                svar_data %>% slice(n()) %>% .$date, sep = " "),
          subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                           "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```

```{r BS22bb, include=FALSE}
svar_data <- fred_md %>%
  dplyr::select(date, MPS_ORTH, LIP, LCPI, EBP, FEDFUNDS) %>%
  mutate(MPS_ORTH = scale(MPS_ORTH)) %>% 
  filter(complete.cases(.), date>=ymd(19821001)) %>%
  mutate_if(is.numeric, ~.x - mean(.x))

irf_ng <- get_irf(y = svar_data %>% dplyr::select(-date),
                   p = 12,
                   type = "both",
                   id.type = "n_gaus",
                   n_ahead = 48,
                   zero_rest = c(1,5))
irf_chol <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "chol",
                    n_ahead = 48)
irf_fevd <- get_irf(y = svar_data %>% dplyr::select(-date),
                    p = 12,
                    type = "both",
                    id.type = "fevd_id",
                    n_ahead = 48,
                    zero_rest = 1)

irf_fnl <- map2(.x = list(irf_chol$irf[,1,,drop=FALSE],
                          irf_ng$irf[,1,,drop=FALSE],
                          irf_ng$irf[,5,,drop=FALSE],
                          irf_fevd$irf[,1,,drop=FALSE]),
                .y = c("surp", "surp", "news", "news"), 
                ~norm_irf(irf_arr = .x, norm_scm = .y, norm_int = 0.25)) %>%
  reduce(abind::abind, along=2)
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, shapiro.test), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))
```

```{r}
rbind(
  stat = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$statistic),
  pval = sapply(apply(irf_ng$resids**2, 2, Box.test, lag = 12), function(x) x$p.value)
) %>% round(4) %>% DT::datatable(colnames = c("MPR", "LIP", "LCPI", "EBP", "FEDFUNDS"))

```

```{r BS22bbb, echo=FALSE}
irf_fnl %>%
  plot_irf(var_name = c("MPR", "LogIP", "LogCPI", "EBP", "FFR"),
           shock_name = c("Surprise (Int-IV)", "Surprise (NG)", "News (NG)", "News (FEVD)")) +
  ggtitle(paste("BS22 shock, sample:", 
                svar_data %>% slice(1) %>% .$date, "--",
                svar_data %>% slice(n()) %>% .$date, sep = " "),
          subtitle = paste("LR-test stat", irf_ng$lratio$`Test statistic` %>% round(4),
                           "w/ pval.", irf_ng$lratio$`p-value` %>% round(4), sep = " "))
```

