---
title: "Model Selection: AIC and BIC"
author: "Bernd Funovits"
output: 
  html_document:
    code_folding: show 
    df_print: paged
    toc: yes
    toc_depth: '3'    
    toc_float:
      collapsed: no
params:
  JOBID: 2021020701
  PATH: "../local_data/p_whf/ukko_bq_jobid_"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pkgs = c("tidyverse")
void = lapply(pkgs, library, character.only = TRUE)
```

# Conclusion

We exclude models whose AIC and/or BIC value is above a certain threshold.
Due to the large number of models, many AIC/BIC values are similar.
Therefore, the analysis in this file should be seen as a preliminary step for model selection which is based on both the AIC/BIC values and the independence properties of the residuals (analysed in the next Rmd file).

# Data Wrangling

The output is in various different files and needs to be joined in one tibble.

```{r}
# All files that were generated on ukko
vec_files = list.files(paste0(params$PATH, params$JOBID))
vec_files = vec_files[grepl("arrayjob", vec_files)]
SCRIPT_PARAMS = readRDS(paste0(params$PATH, params$JOBID, "/", vec_files[1]))[[1]]$results_list$script_params
DIM_OUT = SCRIPT_PARAMS$DIM_OUT

if (file.exists(paste0(params$PATH, params$JOBID, "/",
                       "d_modelselection_aic_bic.rds"))){
  tt_full = readRDS(paste0(params$PATH, params$JOBID, "/",
                                  "d_modelselection_aic_bic.rds")) 
} else {
  tibble_list = vector("list", length(vec_files))
  
  for (ix_file in seq_along(vec_files)){
    file_this = readRDS(paste0(params$PATH, params$JOBID, "/",
                        vec_files[ix_file]))
    
    SCRIPT_PARAMS_this = file_this[[1]]$results_list$script_params
    N_NOISE_PARAMS_SGT = DIM_OUT^2 + DIM_OUT*3
    
    IX_ARRAY_JOB_this = SCRIPT_PARAMS_this$IX_ARRAY_JOB
    N_MODS_this = with(SCRIPT_PARAMS_this, N_MODS_PER_CORE * N_CORES)
    
    tibble_list[[ix_file]] =  
      enframe(file_this) %>% 
      rename(nr = name) %>% 
      mutate(nr = nr + (IX_ARRAY_JOB_this-1)*N_MODS_this) %>% 
      unnest_wider(value) %>% 
      unnest_wider(results_list) %>% 
      select(nr, params_deep_final, value_final, input_integerparams) %>% 
      mutate(n_params = map_int(params_deep_final, length)) %>% 
      mutate(n_params_sys = n_params - N_NOISE_PARAMS_SGT) %>% # SGT has (too) many noise parameters, so I want to check what happens when one uses only the number of system parameters as punishment
      unnest_wider(input_integerparams) %>% 
      mutate(punish_aic = n_params * 2/SCRIPT_PARAMS_this$N_OBS) %>% 
      mutate(punish_bic = n_params * log(SCRIPT_PARAMS_this$N_OBS)/SCRIPT_PARAMS_this$N_OBS) %>% 
      mutate(value_aic = value_final + punish_aic) %>% 
      mutate(value_bic = value_final + punish_bic) %>% 
      select(-value_final, -starts_with("punish"))
  }
  
  tt_full = reduce(tibble_list, bind_rows)
  tt_full = tt_full %>% 
    mutate(p_plus_q = p + q) %>% 
    mutate(n_unstable = kappa * DIM_OUT + k) %>% 
    select(nr, p_plus_q, p ,q, n_unstable, contains("value"), n_params_sys)
  
  saveRDS(tt_full, 
          file = paste0(params$PATH, params$JOBID, "/",
                        "d_modelselection_aic_bic.rds"))
  
}
```

# Analyse AIC

```{r}
DIM_OUT = SCRIPT_PARAMS$DIM_OUT
tt_full %>% 
  arrange(value_aic) %>% 
  mutate_if(is.numeric, round, digits = 4) %>% 
  DT::datatable(extensions = c('Buttons', 'Scroller'), 
                options = list(dom = 'Bflirtp', buttons = I('colvis'), 
                               deferRender = TRUE, scrollY = 350, scroller = TRUE),
                filter = list(position = 'top', clear = TRUE))
```

Group by AR and MA order to check if there is a trend regarding the optimal number of unstable MA roots

```{r}
tt_full %>%
  select(-contains("bic")) %>% 
  arrange(desc(p_plus_q), desc(p), desc(q), value_aic) %>% 
  group_by(p_plus_q) %>% 
  slice(1, .preserve = TRUE) %>% 
  arrange(value_aic)
```

# Plot AIC

## Dependence on sum of AR and MA order

```{r}
tt_full %>% 
  ggplot(aes(x = p_plus_q, y = value_aic, color = as.factor(q))) +
  geom_point() -> pp

plotly::ggplotly(pp)
```

## Dependence on number of unstable roots, colors for different number of system parameters

```{r}
tt_full %>% 
  ggplot(aes(x = n_unstable, y = value_aic, color = as.factor(p_plus_q))) +
  geom_point() -> pp

plotly::ggplotly(pp)
```

## Dependence on sum of AR and MA order

```{r}
tt_full %>% 
  filter(q <= 4, p <= 4) %>% 
  ggplot(aes(x = p_plus_q, y = value_aic, shape = as.factor(p), color = as.factor(q))) +
  geom_point() + 
  scale_shape_discrete(name = "AR and MA \norder (p,q)") +
  scale_color_discrete(name = "") -> pp

plotly::ggplotly(pp)
```

```{r}
tt_full %>% 
  filter(q <= 4, p <= 4) %>% 
  ggplot(aes(x = p_plus_q, y = value_aic, color = as.factor(q), shape = as.factor(p))) +
  geom_point() + 
  scale_color_discrete(name = "MA and MA \norder (q,p)") +
  scale_shape_discrete(name = "") -> pp

plotly::ggplotly(pp)
```

## Dependence on number of unstable roots, colors for different number of system parameters

```{r}
# myfunction <- function(var, string) {
#   print(var)
#   print(string)
#   result <- paste(as.character(string),'_new', sep="")
#   return(result)
# }
# 
# 
# labels = tibble(p = 0:4, q = 0:4)

tt_full %>% 
  filter(p <= 3, q <= 3) %>% 
  ggplot(aes(x = n_unstable, y = value_aic)) +
  geom_point() + facet_grid(p~q, labeller = label_both, scales = "free_y") +
  ggtitle("Dependence of AIC Value w.r.t. Number of MA Roots Inside The Unit Circle") -> pp

plotly::ggplotly(pp)
```

```{r}
tt_full %>% 
  filter(p <= 3, q <= 3) %>% 
  ggplot(aes(x = n_unstable, y = value_aic)) +
  geom_point() + facet_grid(p~q, labeller = label_both) +
  labs(title = "Dependence of AIC Value w.r.t. Integer-Valued Parameters") + 
  theme_bw() + 
  theme(plot.title = element_text(vjust = 1)) +
  ylab("AIC Value") + xlab("Number of MA Roots Inside the Unit Circle")-> pp

ggsave(filename = "../local_data/paper_outputs/AICdependence.eps",
       plot = pp,
       device = "eps")

plotly::ggplotly(pp)


```

# Plot BIC

## Dependence on sum of AR and MA order

```{r}
tt_full %>% 
  ggplot(aes(x = p_plus_q, y = value_aic, color = as.factor(q))) +
  geom_point() -> pp

plotly::ggplotly(pp)
```

## Dependence on number of unstable roots, colors for different number of system parameters

```{r}
tt_full %>% 
  filter(p<=3, q<=3) %>% 
  ggplot(aes(x = n_unstable, y = value_bic, color = as.factor(p_plus_q), shape = as.factor(p_plus_q))) +
  geom_point() +
  theme_bw() + 
  ggtitle("BIC Value w.r.t. Number of MA Roots Inside the Unit Circle") + 
  xlab("Number of MA Roots Inside the Unit Circle") + ylab("BIC Value") + 
  labs(shape = "p plus q") + labs(color = "p plus q") +
  theme(legend.title = element_text(hjust = 0 ,vjust = 0)) -> pp

plotly::ggplotly(pp)
```

## Dependence on sum of AR and MA order

```{r}
tt_full %>% 
  filter(q <= 4, p <= 4) %>% 
  ggplot(aes(x = p_plus_q, y = value_bic, shape = as.factor(p), color = as.factor(q))) +
  geom_point() + 
  scale_shape_discrete(name = "AR and MA \norder (p,q)") +
  scale_color_discrete(name = "") -> pp

plotly::ggplotly(pp)
```

```{r}
tt_full %>% 
  filter(q <= 4, p <= 4) %>% 
  ggplot(aes(x = p_plus_q, y = value_bic, color = as.factor(q), shape = as.factor(p))) +
  geom_point() + 
  scale_color_discrete(name = "MA and MA \norder (q,p)") +
  scale_shape_discrete(name = "") -> pp

plotly::ggplotly(pp)
```

## Dependence on number of unstable roots, colors for different number of system parameters

```{r}
tt_full %>% 
  filter(p <= 3, q <= 3) %>% 
  ggplot(aes(x = n_unstable, y = value_bic)) +
  geom_point() + facet_grid(p~q, labeller = label_both) +
  labs(title = "Dependence of BIC Value w.r.t. Integer-Valued Parameters") + 
  theme_bw() + 
  theme(plot.title = element_text(vjust = 1)) +
  ylab("BIC Value") + xlab("Number of MA Roots Inside the Unit Circle")-> pp

plotly::ggplotly(pp)

ggsave(filename = "../local_data/paper_outputs/BICdependence_bq.eps",
       plot = pp,
       device = "eps")
```

```{r}
tt_full %>% 
  filter(p <= 3, q <= 3) %>% 
  ggplot(aes(x = n_unstable, y = value_aic)) +
  geom_point() + facet_grid(rows = vars(p), cols = vars(q)) -> pp

plotly::ggplotly(pp)
```

