---
title: "Check Residuals"
author: "Bernd Funovits"
output: 
  html_document:
    code_folding: show 
    df_print: paged
    toc: yes
    toc_depth: '3'    
    toc_float:
      collapsed: no
params:
  JOBID: 2021020701
  PATH: "../local_data/p_whf/ukko_bq_jobid_"
  SAVE_AT_END: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pkgs = c("tidyverse", "svarmawhf")
void = lapply(pkgs, library, character.only = TRUE)
```

# Conclusion

In this file, we choose a model based on the ranks regarding AIC/BIC value, and the outcome of the Shapiro-Wilk/Jarque-Bera/Ljung-Box tests.

# Data Wrangling

The computing cluster output is in various different files and needs to be joined in one tibble.

```{r}
# All files that were generated on ukko
vec_files = list.files(paste0(params$PATH, params$JOBID))
vec_files = vec_files[grepl("arrayjob", vec_files)]
SCRIPT_PARAMS = readRDS(paste0(params$PATH, params$JOBID, "/", vec_files[1]))[[1]]$results_list$script_params
DATASET = readRDS(SCRIPT_PARAMS$FILE_NAME_INPUT)
DIM_OUT = SCRIPT_PARAMS$DIM_OUT

pmap_tmpl_whf_rev = function(dim_out = DIM_OUT, p, q, kappa, k, shock_distr = "sgt", ...){
  tmpl_whf_rev(dim_out = DIM_OUT, ARorder = p, MAorder = q, kappa = kappa, k = k, shock_distr = shock_distr)
}

dtable = function(x){
  x %>% 
    select(-shocks) %>% 
    mutate_if(is.numeric, round, digits = 4) %>% 
    DT::datatable(extensions = c('Buttons', 'Scroller'), 
                  options = list(dom = 'Bflirtp', buttons = I('colvis'), 
                                 deferRender = TRUE, scrollY = 350, scrollX = TRUE, scroller = TRUE),
                  filter = list(position = 'top', clear = TRUE))
}
```


```{r}
if (file.exists(paste0(params$PATH, params$JOBID, "/",
                       "e_residualcheck.rds"))){
  tt_full = readRDS(paste0(params$PATH, params$JOBID, "/",
                                  "e_residualcheck.rds")) 
} else {
  tibble_list = vector("list", length(vec_files))
  
  for (ix_file in seq_along(vec_files)){
    file_this = readRDS(paste0(params$PATH, params$JOBID, "/",
                        vec_files[ix_file]))
    
    SCRIPT_PARAMS_this = file_this[[1]]$results_list$script_params
    
    IX_ARRAY_JOB_this = SCRIPT_PARAMS_this$IX_ARRAY_JOB
    N_MODS_this = with(SCRIPT_PARAMS_this, N_MODS_PER_CORE * N_CORES)
    
    tibble_list[[ix_file]] =  
      enframe(file_this) %>% 
      rename(nr = name) %>% 
      mutate(nr = nr + (IX_ARRAY_JOB_this-1)*N_MODS_this) %>% 
      unnest_wider(value) %>% 
      unnest_wider(results_list) %>% 
      select(nr, params_deep_final, value_final, input_integerparams) %>% 
      mutate(n_params = map_int(params_deep_final, length)) %>% 
      unnest_wider(input_integerparams) %>% 
      mutate(punish_aic = n_params * 2/SCRIPT_PARAMS_this$N_OBS) %>% 
      mutate(punish_bic = n_params * log(SCRIPT_PARAMS_this$N_OBS)/SCRIPT_PARAMS_this$N_OBS) %>% 
      mutate(value_aic = value_final + punish_aic) %>% 
      mutate(value_bic = value_final + punish_bic) %>% 
      mutate(tmpl = pmap(., pmap_tmpl_whf_rev)) %>% 
      mutate(res = map2(params_deep_final, tmpl, 
                        ~get_residuals_once(params_deep = .x, 
                                            tmpl = .y,
                                            data_long = DATASET))) %>% 
      mutate(B_mat = map2(params_deep_final, tmpl, 
                        ~fill_tmpl_whf_rev(theta = .x, 
                                            tmpl = .y)$B)) %>% 
      mutate(shocks = map2(res, B_mat, ~ solve(.y, t(.x)) %>% t())) %>% 
      mutate(cov_shocks = map(shocks, function(x){y = abs(cov(x) - diag(DIM_OUT)); names(y) = paste0("cov_el_", letters[1:(DIM_OUT^2)]); y})) %>% 
      unnest_wider(cov_shocks) %>% 
      mutate(cov_el_sum = rowSums(across(contains("cov_el")))) # %>% select(-tmpl, -starts_with("punish"), -res, -B_mat)
  }
  
  tt_full = reduce(tibble_list, bind_rows)
  
  saveRDS(tt_full, 
          file = paste0(params$PATH, params$JOBID, "/",
                        "e_residualcheck.rds"))
  
}
```

# Add Ranks for AIC, BIC, MLE

```{r}
tt = tt_full %>% 
  mutate(rk_aic = rank(value_aic),
         rk_bic = rank(value_bic),
         rk_mle = rank(value_final),
         rk_cov = rank(cov_el_sum)) %>% 
  arrange(value_aic) %>% 
  mutate(p_plus_q = p+q,
         n_unstable = kappa * DIM_OUT + k) %>% 
  select(-params_deep_final, -kappa, -k, -n_params, -contains("punish"), -tmpl, -res, -B_mat) %>% 
  select(nr, p_plus_q, p, q, n_unstable, rk_aic, rk_bic, rk_mle, everything())

tt %>% dtable()
```


# Normality tests

## Shapiro-Wilk Test

For non-Gaussian shock densities, the $H_0$ should be rejected.

```{r}
THRESHOLD_SW = 0.05 

# filter good models by flag == 0
# H_0: Normality -> good models have small p-values
tt = tt %>% 
  mutate(sw = map(shocks, ~apply(.x, 2, FUN = function(x){shapiro.test(x)$p.value}))) %>% 
  mutate(sw_flag = map_int(sw, ~sum(.x > THRESHOLD_SW))) %>% # one component may be Gaussian
  mutate(sw_pval_sum = map_dbl(sw, sum)) %>% 
  unnest_wider(sw, names_sep = "_pval") %>% 
  arrange(desc(sw_pval_sum)) # bad models first

tt %>% dtable()
```



```{r}
tt %>% 
  pull(sw_flag) %>% table()
```

```{r}
tt %>% 
  arrange(desc(sw_pval_sum)) %>% 
  select(rk_aic, rk_mle, sw_flag, everything())
```

## Jarque-Bera Test

For non-Gaussian densities, the Jarque-Bera tests rejects the $H_0$ of normality.

```{r}
THRESHOLD_JB = 0.05 

# filter good moodels by flag == 0
# H_0: Normality -> good models have small p-values
tt = tt %>% 
  mutate(jb = map(shocks, ~apply(.x, 2, FUN = function(x){tsoutliers::JarqueBera.test(x)[[1]]$p.value}))) %>% 
  mutate(jb_flag = map_int(jb, ~sum(.x > THRESHOLD_JB))) %>% # one component may be Gaussian
  mutate(jb_pval_sum = map_dbl(jb, sum)) %>% 
  unnest_wider(jb, names_sep = "_pval") %>% 
  arrange(desc(jb_pval_sum))

tt %>% dtable()
```

```{r}
tt %>% 
  pull(jb_flag) %>% table()
```

```{r}
tt %>% 
  arrange(desc(jb_pval_sum)) %>% 
  select(rk_aic, rk_mle, jb_pval_sum, jb_flag, everything())
```

## Summary for Normality tests

```{r}
tt = tt %>% mutate(normality_flag = sw_flag + jb_flag)
tt %>% pull(normality_flag) %>% table()
```

# Ljung-Box tests: Independent residuals

For residuals, absolute deviations of residuals, squared residuals

```{r}
THRESHOLD_LB = 0.1

# filter good moodels by flag == 0
# H_0: No autocorrelation of (transformation of) residuals
# -> good models have high p-values
tt = tt %>% 
  mutate(lb = map(shocks, ~ apply(.x, 2, FUN = function(x){Box.test(x, lag = 8)$p.value }))) %>% 
  mutate(lb_flag = map_lgl(lb, ~any(.x < THRESHOLD_LB))) %>% 
  mutate(lb_pval_sum = map_dbl(lb, sum)) %>%
  unnest_wider(lb, names_sep = "_pval") %>% 
  
  mutate(lb_abs = map(shocks, ~ apply(.x, 2, FUN = function(x){Box.test(abs(x), lag = 8)$p.value }))) %>% 
  mutate(lb_abs_flag = map_lgl(lb_abs, ~any(.x < THRESHOLD_LB))) %>% 
  mutate(lb_abs_pval_sum = map_dbl(lb_abs, sum)) %>%
  unnest_wider(lb_abs, names_sep = "_pval") %>% 
  
  mutate(lb_sq = map(shocks, ~ apply(.x, 2, FUN = function(x){Box.test(x^2, lag = 8)$p.value }))) %>% 
  mutate(lb_sq_flag = map_lgl(lb_sq, ~any(.x < THRESHOLD_LB))) %>% 
  mutate(lb_sq_pval_sum = map_dbl(lb_sq, sum)) %>%
  unnest_wider(lb_sq, names_sep = "_pval") %>% 

  mutate(lb_all_pval_sum = lb_pval_sum + lb_abs_pval_sum + lb_sq_pval_sum) %>% 
  arrange(lb_all_pval_sum)
```

## Summary

```{r}
tt = tt %>% mutate(indep_flag = lb_flag + lb_abs_flag + lb_sq_flag)
tt %>%  pull(indep_flag) %>% table()
```




# Analysis

```{r}
tt %>% 
  select(p_plus_q, p, q, n_unstable, 
         contains("rk_"), normality_flag, lb_flag, indep_flag, 
         contains("pval"), contains("sum"), contains("flag"), everything()) %>% 
  dtable()

```

```{r}
tt %>% 
  filter(sw_flag == 0) %>% 
  filter(lb_flag == 0) %>% 
  filter(lb_abs_flag == 0) %>% 
  filter(lb_sq_flag == 0) %>% 
  filter(jb_flag == 0) %>% 
  arrange(value_bic) %>% 
  dtable()
```

```{r}
tt %>% pull(normality_flag) %>% table()

```

```{r}
tt %>% pull(indep_flag) %>% table()
```

```{r}
tt = tt %>% mutate(norm_indep_flag = normality_flag + indep_flag)
tt %>% pull(norm_indep_flag) %>% table()
```

```{r}
tt = tt %>% 
  left_join(tt_full %>% select(nr, params_deep_final, tmpl, kappa, k),
            by = "nr")

if(params$SAVE_AT_END){
  saveRDS(tt,
          file = paste0(params$PATH, params$JOBID, "/",
                        "e_residualcheck_end.rds"))
}

```

