---
title: "Robust Standard Errors"
author: "Bernd Funovits"
output: 
  html_document:
    code_folding: show  
    df_print: paged
    toc: yes
    toc_depth: '3'    
    toc_float:
      collapsed: no 
    number_sections: true
params:
  DIRPATH_MOD: "../local_data/p_whf/best_mod_rob/"
  FILEPATH_DATASET: "../local_data/g_gmr_bq/data_xts.rds"
  ZERO_RESTR: FALSE 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = TRUE)
pkgs = c("svarmawhf", "svars", "tidyverse", "numDeriv", "glue", "corrplot")
void = lapply(pkgs, library, character.only = TRUE)

#Pseudo Inverse
ginv = MASS::ginv 

dtable = function(x){
  x %>% 
    select(-where(is.list)) %>% 
    mutate_if(is.numeric, round, digits = 7) %>% 
    DT::datatable(extensions = c('Buttons', 'Scroller', 'ColReorder'), 
                  options = list(dom = 'Bflirtp', buttons = I('colvis'), 
                                 deferRender = TRUE, scrollY = 350, scrollX = TRUE, scroller = TRUE,
                                 colReorder = TRUE),
                  filter = list(position = 'top', clear = TRUE)) %>% 
    suppressWarnings()
}

```

# High Level Summary

We obtain different estimates for the standard deviations of the parameter estimates.
In particular, we compare estimates under the assumption of correct model specification with robust ones.

Under correct specification, the information matrix matrix may be calculated as the 

* outer product gradient (OPG) of the scores
* the Hessian obtained as output for `stats::optim()`
* the analytic version of the Hessian obtained from `numDeriv::hessian()`

Allowing for misspecification, the robust standard errors are obtained from the covariance matrix $\Omega^{-1}\left(\hat{\theta_T}\right) I\left(\hat{\theta_T}\right) \Omega^{-1}\left(\hat{\theta_T}\right)$.
Again, the Hessian may be calculated as output of `stats::optim()` or in an analytic way from `numDeriv::hessian()`.

First, we investigate the OPG and the different versions of the Hessians quantitatively and by plotting the values, see section [OPG and Hessian] and in particular [Plot Parameters].
Subsequently, we compare the diagonal elements of the OPG and the different versions of the Hessian in [Diagonal Elements].
Next, we evaluate the implied standard deviations for the system and noise parameters quantitatively and with plots in [Compare Standard Deviations].
Finally, we provide the results, i.e. each part of the parameter estimates together with their robust and non-robust standard errors, see [Results].

Some distribution parameters are not estimated very precisely as one can see from [Noise Parameters].
The sub-matrix pertaining to the distribution parameters is close to singular.

# Load data

## Data Set

Load Blanchard and Quah (1989) dataset and its dimensions.

```{r}
DATASET = readRDS(params$FILEPATH_DATASET) %>% 
  as.matrix()
DIM_OUT = dim(DATASET)[2]
N_OBS = dim(DATASET)[1]
```


## Optimal model

Load the template and the deep parameters for the best model.

```{r}
PARAMS = read_rds(glue("{params$DIRPATH_MOD}bf_params_12_2.rds"))
TMPL = read_rds(glue("{params$DIRPATH_MOD}bf_tmpl_12_2.rds"))
```

Fill the template

```{r}
params_opt_mod = fill_tmpl_whf_rev(theta = PARAMS,
                                   tmpl = TMPL)
```

Print AR parameters in wide matrix format.

```{r}
params_opt_mod$polm_ar %>% matrix(nrow = 2)
```

Print MA backwards parameters in wide matrix format.

```{r}
params_opt_mod$polm_ma_bwd %>% matrix(nrow = 2)
```

Print MA forwards parameters in wide matrix format.

```{r}
params_opt_mod$polm_ma_fwd %>% matrix(nrow = 2)
```

Print static matrix B

```{r}
params_opt_mod$B %>% matrix(nrow = 2)
```

Print distribution parameters, $\lambda, p, q$ for each variable (in columns)

```{r}
params_opt_mod$distr %>% matrix(ncol = 2)
```

Number of deep parameters parameters 

```{r}
TMPL$ar$n_par
TMPL$ma_bwd$n_par
TMPL$ma_fwd$n_par
TMPL$B$n_par
TMPL$distr$n_par
```

## Indices of System and Noise Parameters

```{r}
ix_params_sys = 1:12
ix_params_sys_ar = 1:4
ix_params_sys_ma_bwd = 5:8
ix_params_sys_ma_fwd = 9:12
```

```{r}
ix_params_noise = 13:22
ix_params_noise_b = 13:16
ix_params_noise_sgt = 17:22
```

## Likelihood function

Obtain likelihood function for given dataset and template.


```{r}
ll_fun_sgt = ll_whf_factory(data_wide = t(DATASET), 
                            tmpl = TMPL, shock_distr = "sgt", 
                            use_cpp = TRUE)
```

Recalculate the optimisation with argument `hessian = TRUE`.

```{r}
N_PARAMS = length(PARAMS)

out = optim(par = PARAMS, 
            fn = ll_fun_sgt, 
            method = "L-BFGS-B", 
            lower = c(rep(-Inf, N_PARAMS), rep(c(-1, 1.5, 2), DIM_OUT)),
            upper = c(rep(Inf, N_PARAMS), rep(c(1, Inf, Inf), DIM_OUT)),
            control = list(maxit = 100), hessian = TRUE)
```

Check output 

```{r}
out$par - PARAMS
```


# OPG and Hessian

## Obtain Different Versions

Calculate OPG

```{r}
ll_grad = ll_whf_factory_grad_helper(data_wide = t(DATASET),
                                     tmpl = TMPL)
```

```{r}
J = jacobian(func = ll_grad,
             x = PARAMS)
opg = J/sqrt(N_OBS)
opg = crossprod(opg)

if(params$ZERO_RESTR){
  opg[ix_params_sys, ix_params_noise] = 0
  opg[ix_params_noise, ix_params_sys] = 0
}

opg_inv = ginv(opg)
```

Calculate Analytic Hessian with **numDeriv** package.

```{r}
ha = hessian(func = ll_fun_sgt,
             x = PARAMS)

if(params$ZERO_RESTR){
  ha[ix_params_sys, ix_params_noise] = 0
  ha[ix_params_noise, ix_params_sys] = 0
}

ha_inv = ginv(ha)
```

Calculate Hessian via **optim**

```{r}
hopt = out$hessian

if(params$ZERO_RESTR){
  hopt[ix_params_sys, ix_params_noise] = 0
  hopt[ix_params_noise, ix_params_sys] = 0
}

hopt_inv = ginv(hopt)
```

## Plot Parameters

Hessian (inverse of information matrix under correct specification) and its normalised version.

In the first column are the 

* OPG
* Analytic Hessian
* Hessian obtain from optim

and in the second column their normalised versions.

```{r fig.height=11.2, fig.width=7}
par(mfcol = c(3,2))

opg %>% corrplot(is.corr = FALSE)
ha %>% corrplot(is.corr = FALSE)
hopt %>% corrplot(is.corr = FALSE)
opg %>% cov2cor() %>% corrplot() %>% suppressWarnings()
ha %>% cov2cor() %>% corrplot() %>% suppressWarnings()
hopt %>% cov2cor() %>% corrplot() %>% suppressWarnings()
```

### System Paramters

```{r fig.height=11.2, fig.width=7}
par(mfcol = c(3,2))

opg[ix_params_sys, ix_params_sys] %>% corrplot(is.corr = FALSE)
ha[ix_params_sys, ix_params_sys] %>% corrplot(is.corr = FALSE)
hopt[ix_params_sys, ix_params_sys] %>% corrplot(is.corr = FALSE)
opg[ix_params_sys, ix_params_sys] %>% cov2cor() %>% corrplot() %>% suppressWarnings()
ha[ix_params_sys, ix_params_sys] %>% cov2cor() %>% corrplot() %>% suppressWarnings()
hopt[ix_params_sys, ix_params_sys] %>%cov2cor() %>% corrplot() %>% suppressWarnings()
```

### Noise Parameters

#### Noise Parameters with Strict Zeros

```{r}
opg[ix_params_sys, ix_params_noise] = 0
opg[ix_params_noise, ix_params_sys] = 0

opg[ix_params_noise_b, ix_params_noise_sgt] = 0
opg[ix_params_noise_sgt, ix_params_noise_b] = 0

opg[ix_params_noise_sgt[1:3], ix_params_noise_sgt[4:6]] = 0
opg[ix_params_noise_sgt[4:6], ix_params_noise_sgt[1:3]] = 0

opg %>% zapsmall()
opg %>% ginv() %>% zapsmall()
```

```{r}
hopt[ix_params_sys, ix_params_noise] = 0
hopt[ix_params_noise, ix_params_sys] = 0

hopt[ix_params_noise_b, ix_params_noise_sgt] = 0
hopt[ix_params_noise_sgt, ix_params_noise_b] = 0

hopt[ix_params_noise_sgt[1:3], ix_params_noise_sgt[4:6]] = 0
hopt[ix_params_noise_sgt[4:6], ix_params_noise_sgt[1:3]] = 0

hopt %>% zapsmall()
hopt %>% ginv() %>% zapsmall()
```

```{r}
ha[ix_params_sys, ix_params_noise] = 0
ha[ix_params_noise, ix_params_sys] = 0

ha[ix_params_noise_b, ix_params_noise_sgt] = 0
ha[ix_params_noise_sgt, ix_params_noise_b] = 0

ha[ix_params_noise_sgt[1:3], ix_params_noise_sgt[4:6]] = 0
ha[ix_params_noise_sgt[4:6], ix_params_noise_sgt[1:3]] = 0

ha %>% zapsmall()
ha %>% ginv() %>% zapsmall()
```


```{r}
c(opg[ix_params_noise, ix_params_noise], 
  ha[ix_params_noise, ix_params_noise], 
  hopt[ix_params_noise, ix_params_noise]) %>% 
  array(dim = c(10, 10, 3)) %>% 
  zapsmall()
```


```{r}
hopt[ix_params_noise, ix_params_noise] %>% ginv() %>% zapsmall()
```
```{r}
hopt[ix_params_noise_sgt, ix_params_noise_sgt] %>% ginv() %>% zapsmall()
```

```{r}
eigen(hopt[ix_params_noise, ix_params_noise])$values
```


```{r}
eigen(hopt[ix_params_noise, ix_params_noise])$values
```
```{r}
eigen(hopt[ix_params_noise_b, ix_params_noise_b])$values
```
```{r}
eigen(hopt[ix_params_noise_sgt, ix_params_noise_sgt])$values
```
```{r}
eigen(hopt[ix_params_noise_sgt[1:3], ix_params_noise_sgt[1:3]])$values
```


```{r}
hopt[ix_params_noise_sgt[1:3], ix_params_noise_sgt[1:3]] %>% zapsmall()
hopt[ix_params_noise_sgt[1:3], ix_params_noise_sgt[1:3]] %>% ginv() %>% zapsmall()
```

```{r}
eigen(hopt[ix_params_noise_sgt[4:6], ix_params_noise_sgt[4:6]])$values
```

```{r}
hopt[ix_params_noise_sgt[4:6], ix_params_noise_sgt[4:6]] %>% zapsmall()
hopt[ix_params_noise_sgt[4:6], ix_params_noise_sgt[4:6]] %>% ginv() %>% zapsmall()
```

```{r fig.height=11.2, fig.width=7}
par(mfcol = c(3,2))

opg[ix_params_noise, ix_params_noise] %>% corrplot(is.corr = FALSE)
ha[ix_params_noise, ix_params_noise] %>% corrplot(is.corr = FALSE)
hopt[ix_params_noise, ix_params_noise] %>% corrplot(is.corr = FALSE)
opg[ix_params_noise, ix_params_noise] %>% cov2cor() %>% corrplot() %>% suppressWarnings()
ha[ix_params_noise, ix_params_noise] %>% cov2cor() %>% corrplot() %>% suppressWarnings()
hopt[ix_params_noise, ix_params_noise] %>%cov2cor() %>% corrplot() %>% suppressWarnings()
```



B matrix

```{r fig.height=11.2, fig.width=7}
par(mfcol = c(3,2))

opg[ix_params_noise_b, ix_params_noise_b] %>% corrplot(is.corr = FALSE)
ha[ix_params_noise_b, ix_params_noise_b] %>% corrplot(is.corr = FALSE)
hopt[ix_params_noise_b, ix_params_noise_b] %>% corrplot(is.corr = FALSE)
opg[ix_params_noise_b, ix_params_noise_b] %>% cov2cor() %>% corrplot() %>% suppressWarnings()
ha[ix_params_noise_b, ix_params_noise_b] %>% cov2cor() %>% corrplot() %>% suppressWarnings()
hopt[ix_params_noise_b, ix_params_noise_b] %>%cov2cor() %>% corrplot() %>% suppressWarnings()
```

Distribution parameters

```{r fig.height=11.2, fig.width=7}
par(mfcol = c(3,2))

opg[ix_params_noise_sgt, ix_params_noise_sgt] %>% corrplot(is.corr = FALSE)
ha[ix_params_noise_sgt, ix_params_noise_sgt] %>% corrplot(is.corr = FALSE)
hopt[ix_params_noise_sgt, ix_params_noise_sgt] %>% corrplot(is.corr = FALSE)
opg[ix_params_noise_sgt, ix_params_noise_sgt] %>% cov2cor() %>% corrplot() %>% suppressWarnings()
ha[ix_params_noise_sgt, ix_params_noise_sgt] %>% cov2cor() %>% corrplot() %>% suppressWarnings()
hopt[ix_params_noise_sgt, ix_params_noise_sgt] %>%cov2cor() %>% corrplot() %>% suppressWarnings()
```


## Diagonal elemets

We compare the diagonal elements of

* the OPG matrix
* Hessian obtained from optim
* analytic Hessian 

### Quantitative 

The columns starting with **diff_** contain the absolute difference between the different objects 

```{r}
(
  comp_diag = tibble(name = c(rep("AR", 4),
                              rep("MA_bwd", 4),
                              rep("MA_fwd", 4),
                              rep("B", 4),
                              rep("distr", 6)),
                     type = c(rep("system", 12), 
                              rep("noise", 10)),
                     a_opg_diag = diag(opg),
                     b_ha_diag = diag(ha),
                     c_hopt_diag = diag(hopt))
)
```
```{r}
comp_diag %>% 
  dtable()
```

We need the following helper function which calculates the sum of the absolute differences between the elements pertaining to (OPG, Hessian optim, Hessian analytic)

```{r}
obtain_diff_abs_mat = function(df){
  
  mat  = df %>% 
    as.matrix()
  
  names_df = colnames(df)
  
  res = matrix(nrow = ncol(df), ncol = ncol(df))
  
  for (ix_row in 1:ncol(df)){
    for (ix_col in 1:ncol(df)) {
      res[ix_row, ix_col] = (mat[, ix_row] - mat[, ix_col]) %>% abs() %>% sum(na.rm = TRUE)
    }
  }
  
  rownames(res) = names_df
  colnames(res) = names_df
  
  return(res)
}
```


Investigate the differences between the diagonal elements for each group (AR, MA backwards, MA forwards, B, distribution).

```{r}
comp_diag %>% select(contains("diag")) %>% obtain_diff_abs_mat()
```

### Plots

Plot AR parameters

```{r}
comp_diag %>% 
  filter(name == "AR") %>% 
  rowid_to_column() %>% 
  select(-contains("diff")) %>% 
  select(-name, -type) %>% 
  pivot_longer(-rowid) %>% 
  ggplot(aes(x = rowid, y = value, fill = name)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Diagonal Elements for System Parameters: AR")
```

Plot MA backwards parameters

```{r}
comp_diag %>% 
  filter(name == "MA_bwd") %>% 
  rowid_to_column() %>% 
  select(-contains("diff")) %>% 
  select(-name, -type) %>% 
  pivot_longer(-rowid) %>% 
  ggplot(aes(x = rowid, y = value, fill = name)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Diagonal Elements for System Parameters: MA backwards")
```

Plot MA forwards parameters

```{r}
comp_diag %>% 
  filter(name == "MA_fwd") %>% 
  rowid_to_column() %>% 
  select(-contains("diff")) %>% 
  select(-name, -type) %>% 
  pivot_longer(-rowid) %>% 
  ggplot(aes(x = rowid, y = value, fill = name)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Diagonal Elements for System Parameters: MA forwards")
```

Plot noise parameters

```{r}
comp_diag %>% 
  filter(name == "B") %>% 
  rowid_to_column() %>% 
  select(-contains("diff")) %>% 
  select(-name, -type) %>% 
  pivot_longer(-rowid) %>% 
  ggplot(aes(x = rowid, y = value, fill = name)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Diagonal Elements for Noise Parameters: B")
```

```{r}
comp_diag %>% 
  filter(name == "distr") %>% 
  rowid_to_column() %>% 
  select(-contains("diff")) %>% 
  select(-name, -type) %>% 
  pivot_longer(-rowid) %>% 
  ggplot(aes(x = rowid, y = value, fill = name)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Diagonal Elements for Noise Parameters: Distribution")
```

```{r}
hopt %>% diag() %>% sqrt()
```


# Compare Standard Deviations

## Quantitative

Difference between all possible options for calculating the standard deviations of the parameters.

```{r}
comp_sd = tibble(name = c(rep("AR", 4),
                          rep("MA_bwd", 4),
                          rep("MA_fwd", 4),
                          rep("B", 4),
                          rep("distr", 6)),
                 type = c(rep("system", 12), 
                          rep("noise", 10))) %>% 
  unite("type_name", type, name, remove = FALSE) %>% 
  mutate(aa_opg_inv  = diag(ginv(opg)) %>% sqrt(),
         ab_hopt_inv = diag(ginv(hopt)) %>% sqrt(),
         ac_ha_inv   = diag(ginv(ha)) %>% sqrt(),
         ba_rob_hopt = diag(ginv(hopt) %*% opg %*% ginv(hopt)) %>% sqrt(),
         bb_rob_ha   = diag(ginv(ha) %*% opg %*% ginv(ha)) %>% sqrt())
```


```{r}
comp_sd %>% 
  mutate(across(where(is.numeric), ~ round(.x, digits = 3))) %>% 
  dtable()
```


```{r}
comp_sd %>% 
  select(starts_with("a"), starts_with("b")) %>% 
  obtain_diff_abs_mat()

```

```{r}
comp_sd %>% 
  filter(type == "system") %>% 
  select(starts_with("a"), starts_with("b")) %>% 
  obtain_diff_abs_mat()

```

```{r}
comp_sd %>% 
  filter(type == "noise") %>% 
  select(starts_with("a"), starts_with("b")) %>% 
  obtain_diff_abs_mat()

```

```{r}
comp_sd %>% 
  filter(name == "B") %>% 
  select(starts_with("a"), starts_with("b")) %>% 
  obtain_diff_abs_mat()

```

```{r}
comp_sd %>% 
  filter(name == "distr") %>% 
  select(starts_with("a"), starts_with("b")) %>% 
  obtain_diff_abs_mat()

```

## Plots

```{r}
comp_sd %>% 
  filter(name == "AR") %>% 
  rowid_to_column() %>% 
  select(-contains("diff")) %>% 
  select(-name, -type, -type_name) %>% 
  pivot_longer(-rowid) %>% 
  ggplot(aes(x = rowid, y = value, fill = name)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Standard Errors of AR Parameters")
```

```{r}
comp_sd %>% 
  filter(name == "MA_bwd") %>% 
  rowid_to_column() %>% 
  select(-contains("diff")) %>% 
  select(-name, -type, -type_name) %>% 
  pivot_longer(-rowid) %>% 
  ggplot(aes(x = rowid, y = value, fill = name)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Standard Errors of MA backwards Parameters")
```

```{r}
comp_sd %>% 
  filter(name == "MA_fwd") %>% 
  rowid_to_column() %>% 
  select(-contains("diff")) %>% 
  select(-name, -type, -type_name) %>% 
  pivot_longer(-rowid) %>% 
  ggplot(aes(x = rowid, y = value, fill = name)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Standard Errors of MA forwards Parameters")
```

```{r}
comp_sd %>% 
  filter(name == "B") %>% 
  rowid_to_column() %>% 
  select(-contains("diff")) %>% 
  select(-name, -type, -type_name) %>% 
  pivot_longer(-rowid) %>% 
  ggplot(aes(x = rowid, y = value, fill = name)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Standard Errors of B Parameters")
```
```{r}
PARAMS[ix_params_noise_sgt]
```


```{r}
comp_sd %>% 
  filter(name == "distr") %>% 
  rowid_to_column() %>% 
  select(-contains("diff")) %>% 
  select(-name, -type, -type_name) %>% 
  pivot_longer(-rowid) %>% 
  ggplot(aes(x = rowid, y = value, fill = name)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Standard Errors of Distribution Parameters")
```


# Results

We choose the OPG for standard deviations in the correctly specified setting and the robust version calculated with analytic Hessian in the misspecified setting

```{r}
opt_mod_params = fill_tmpl_whf_rev(theta = PARAMS,
                                   tmpl = TMPL)
opt_mod_sd_correctlyspecified = fill_tmpl_whf_rev(theta = comp_sd %>% pull(aa_opg_inv),
                                                  tmpl = TMPL)
opt_mod_sd_misspecified = fill_tmpl_whf_rev(theta = comp_sd %>% pull(ba_rob_hopt),
                                            tmpl = TMPL)
```

Print AR parameters with non-robust and robust standard errors in wide matrix format.

```{r}
opt_mod_params$polm_ar %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_correctlyspecified$polm_ar %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_misspecified$polm_ar %>% matrix(nrow = 2) %>% round(digits = 3)
```

Print MA backwards parameters with non-robust and robust standard errors in wide matrix format.

```{r}
opt_mod_params$polm_ma_bwd %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_correctlyspecified$polm_ma_bwd %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_misspecified$polm_ma_bwd %>% matrix(nrow = 2) %>% round(digits = 3)
```

Print MA forwards parameters with non-robust and robust standard errors in wide matrix format.

```{r}
opt_mod_params$polm_ma_fwd %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_correctlyspecified$polm_ma_fwd %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_misspecified$polm_ma_fwd %>% matrix(nrow = 2) %>% round(digits = 3)
```

Print static matrix B with non-robust and robust standard errors.

```{r}
opt_mod_params$B %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_correctlyspecified$B %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_misspecified$B %>% matrix(nrow = 2) %>% round(digits = 3)
```

Print distribution parameters with non-robust and robust standard errors , $\lambda, p, q$, for each variable (in columns)

```{r}
opt_mod_params$distr %>% matrix(ncol = 2) %>% round(digits = 3)
opt_mod_sd_correctlyspecified$distr %>% matrix(ncol = 2) %>% round(digits = 3)
opt_mod_sd_misspecified$distr %>% matrix(ncol = 2) %>% round(digits = 3)
```

## Alternative Option

Under correct specification may also choose, e.g., the analytic version of the Hessian to obtain the information matrix and calculate a robust version by using again the analytic version of the Hessian as well as the OPG

```{r}
opt_mod_params = fill_tmpl_whf_rev(theta = PARAMS,
                                   tmpl = TMPL)
opt_mod_sd_correctlyspecified_alt = fill_tmpl_whf_rev(theta = comp_sd %>% pull(ac_ha_inv),
                                                  tmpl = TMPL)
opt_mod_sd_misspecified_alt = fill_tmpl_whf_rev(theta = comp_sd %>% pull(bb_rob_ha),
                                            tmpl = TMPL)
```

Print AR parameters with non-robust and robust standard errors in wide matrix format.

```{r}
opt_mod_params$polm_ar %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_correctlyspecified_alt$polm_ar %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_misspecified_alt$polm_ar %>% matrix(nrow = 2) %>% round(digits = 3)
```

Print MA backwards parameters with non-robust and robust standard errors in wide matrix format.

```{r}
opt_mod_params$polm_ma_bwd %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_correctlyspecified_alt$polm_ma_bwd %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_misspecified_alt$polm_ma_bwd %>% matrix(nrow = 2) %>% round(digits = 3)
```

Print MA forwards parameters with non-robust and robust standard errors in wide matrix format.

```{r}
opt_mod_params$polm_ma_fwd %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_correctlyspecified_alt$polm_ma_fwd %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_misspecified_alt$polm_ma_fwd %>% matrix(nrow = 2) %>% round(digits = 3)
```

Print static matrix B with non-robust and robust standard errors.

```{r}
opt_mod_params$B %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_correctlyspecified_alt$B %>% matrix(nrow = 2) %>% round(digits = 3)
opt_mod_sd_misspecified_alt$B %>% matrix(nrow = 2) %>% round(digits = 3)
```

Print distribution parameters with non-robust and robust standard errors , $\lambda, p, q$, for each variable (in columns)

```{r}
opt_mod_params$distr %>% matrix(ncol = 2) %>% round(digits = 3)
opt_mod_sd_correctlyspecified_alt$distr %>% matrix(ncol = 2) %>% round(digits = 3)
opt_mod_sd_misspecified_alt$distr %>% matrix(ncol = 2) %>% round(digits = 3)
```
# Skewness and Kurtosis

```{r}
sgt_skewness = function(l, p, q){
  v = q^(-1/p) *
    (
      (3*l^2+1) *
        (beta(3/p,q-2/p)/beta(1/p,q)) -
        4*l^2 *
        (beta(2/p,q-1/p)/beta(1/p,q))^2
    )^(-1/2)
  
  skewness = 2 * q^(3/p) * l * v^3 / beta(1/p, q)^3 *
    (8*l^2*beta(2/p,q-1/p)^3 - 
       3*(1+3*l^2) * beta(1/p,q) * beta(2/p, q-1/p) * beta(3/p,q-2/p) + 
       2 * (1+l^2) * beta(1/p,q)^2 * beta(4/p, q-3/p)
       )
  
  return(skewness)
}

sgt_kurtosis = function(l, p, q){
  v = q^(-1/p) *
    (
      (3*l^2+1) *
        (beta(3/p,q-2/p)/beta(1/p,q)) -
        4*l^2 *
        (beta(2/p,q-1/p)/beta(1/p,q))^2
    )^(-1/2)
  
  kurtosis = q^(4/p) * v^4 / beta(1/p, q)^4 *
    (48*l^4*beta(2/p,q-1/p)^4 +
       24 * l^2 * (1+3*l^2) * beta(1/p,q) * beta(2/p, q-1/p)^2 * beta(3/p,q-2/p) -
       32 * l^2 * (1+l^2) * beta(1/p,q)^2 * beta(2/p, q-1/p) * beta(4/p,q-3/p) + 
       (1+10*l^2+5*l^4) * beta(1/p,q)^3 * beta(5/p, q-4/p)
    )
  
  return(kurtosis)
}
```


```{r}
sgt_skewness(-0.52,1.49,85616)
sgt_kurtosis(-0.52,1.49,85616)
```


```{r}
sgt_skewness(0.15,1.92,7.89)
sgt_kurtosis(0.15,1.92,7.89)
```

